A prototype software framework for transferable computational health economic models and its early application in youth mental health

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
ready for comparison

names_chr <- names(df)
# df <- data.frame(df[,1],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
#                      nrow(df)),
#                  df[,2#:3
#                     ],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
#                      ,nrow(df)),
#                  #df[,4],
#                  #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
#                  df[,3#5
#                     ])
# colnames(df) <- c("Library",
#                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
#                   #"Ref", 
#                   "Purpose", 
#                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
#                   #"Standard     ",# " ",
#                   "R library dependencies")
#df$Library <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
#df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>% #[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    #df$Ref<-NULL
    #df$Library <- ""
    # df$Library  <- df$Library %>% 
    #                   purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Library <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    #df[,c(1,3,5:6)]   %>%
    df %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m")
    }
```

>>>>

names_chr <- names(df)
# df <- data.frame(df[,1],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
#                      nrow(df)),
#                  df[,2#:3
#                     ],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
#                      ,nrow(df)),
#                  #df[,4],
#                  #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
#                  df[,3#5
#                     ])
# colnames(df) <- c("Library",
#                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
#                   #"Ref", 
#                   "Purpose", 
#                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
#                   #"Standard     ",# " ",
#                   "R library dependencies")
#df$Library <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
#df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>% #[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    #df$Ref<-NULL
    #df$Library <- ""
    # df$Library  <- df$Library %>% 
    #                   purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Library <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    #df[,c(1,3,5:6)]   %>%
    df %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      linesep = "\\addlinespace",
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m") %>%
      kableExtra::kable_styling(latex_options = "striped")
    }
```

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Tables_3b.Rmd
ready for comparison

names_chr <- names(df)
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>% 
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    df %>%
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m")
    }
```

>>>>

names_chr <- names(df)
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>% 
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    df %>%
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      linesep = "\\addlinespace",
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m") %>%
      kableExtra::kable_styling(latex_options = "striped")
    }
```

### 2024-03-01 Markdown/Manuscript/Parent_PDF/Springer.Rmd
ready for comparison

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: School of Public Health and Preventive Medicine
      orgname: Monash University
    address:
        #street: "553 St Kilda Road"
        city: Melbourne
        #postcode: 3004
        #state: Victoria
        country: Australia
  - number: 2
    corresponding: FALSE
    info:
      orgname: Orygen
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
        #state: Victoria
        country: Australia
  - number: 3
    corresponding: FALSE
    info:
      orgdiv: Centre for Youth Mental Health
      orgname: The University of Melbourne
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
    #   state: Victoria
        country: Australia
  - number: 4
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Heart Foundation      
    address:
     #   street: "2/850 Collins St"
        city: Docklands
        # postcode: 3008
     #   state: Victoria
        country: Australia
  - number: 5
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: headspace National Youth Mental Health Foundation   
    address:
    #  #   street: "485 La Trobe St"
        city: Melbourne
    #     postcode: 3000
    #  #   state: Victoria
        country: Australia     
  - number: 6
    corresponding: FALSE
    info:
      orgdiv: Institute for Health and Sport
      orgname: Victoria University 
    address:
    #  #   street: "70/104 Ballarat Rd"
        city: Footscray
    #     postcode: 3011
    #  #   state: Victoria
        country: Australia 
      # 
  - number: 7
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Flinders University   
    address:
    #     # street: "182 Victoria Square"     
        city: Adelaide
    #     postcode: 5000
    #  #   state: South Australia
        country: Australia 
keywords:  
  - adolescence
  - computational models
  - health economics
  - mental disorders
  - open-source models
  - software frameworks

>>>>

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: School of Public Health and Preventive Medicine
      orgname: Monash University
    address:
        #street: "553 St Kilda Road"
        city: Melbourne
        #postcode: 3004
        #state: Victoria
        country: Australia
  - number: 2
    corresponding: FALSE
    info:
      orgname: Orygen
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
        #state: Victoria
        country: Australia
  - number: 3
    corresponding: FALSE
    info:
      orgdiv: Centre for Youth Mental Health
      orgname: The University of Melbourne
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
    #   state: Victoria
        country: Australia
  - number: 4
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Heart Foundation      
    address:
     #   street: "2/850 Collins St"
        city: Docklands
        # postcode: 3008
     #   state: Victoria
        country: Australia
  - number: 5
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: headspace National Youth Mental Health Foundation   
    address:
    #  #   street: "485 La Trobe St"
        city: Melbourne
    #     postcode: 3000
    #  #   state: Victoria
        country: Australia     
  - number: 6
    corresponding: FALSE
    info:
      orgdiv: Institute for Health and Sport
      orgname: Victoria University 
    address:
    #  #   street: "70/104 Ballarat Rd"
        city: Footscray
    #     postcode: 3011
    #  #   state: Victoria
        country: Australia 
      # 
  - number: 7
    corresponding: FALSE
    info:
      orgdiv: Flinders Health and Medical Research Institute
      orgname: Flinders University   
    address:
    #     # street: "182 Victoria Square"     
        city: Adelaide
    #     postcode: 5000
    #  #   state: South Australia
        country: Australia 
keywords:  
  - adolescence
  - computational models
  - health economics
  - mental disorders
  - open-source models
  - software frameworks
